Update Meeting: 11-11-2021

### 2021-11-22 analysis/update_meeting_11_11_2021.Rmd
wflow_publish("analysis/update_meeting_11_11_2021.Rmd")

options(scipen=999)
source("code/settings.R")
source("R/functions.R")
library(targets)
library(dplyr)
library(DT)
library(knitr)
library(ggplot2)
library(kableExtra)

@@

```{r proxyMR_figure_adj, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), out.width = "200%", dpi=600}
proxyMR_prod_comparison_fig_yiyp_adj
```

@@

```{r regression_summary, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), out.width = "200%", dpi=600}
data <- proxyMR_comparison_summary_yiyp_adj_joint
summary(lm(rho_beta ~ omega_beta + 0, data = data))
summary(lm(gam_beta ~ omega_beta + 0, data = data))
summary(lm(gam_rho_beta ~ omega_beta + 0, data = data))
```

```{r resid_summary, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), out.width = "200%", dpi=600}
rho_resid <- resid(lm(rho_beta ~ gam_beta, data = data))
data$gam_rho_resid <- rho_resid + data$gam_beta
summary(lm(gam_rho_resid ~ omega_beta + 0, data = data))
```

```{r proxyMR_fsig_omega_vs_gam, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), out.width = "200%", dpi=600, message = FALSE, warning = FALSE}

@@

>>>>

options(scipen=999)
source("code/settings.R")
source("R/functions.R")
library(targets)
library(dplyr)
library(DT)
library(knitr)
library(ggplot2)
library(kableExtra)
library(cowplot)

@@

```{r YiYp_adj_model, echo = FALSE}
library(knitr)
knitr::include_graphics("assets/two_trait_model_yiyp_adj.png", error = FALSE)
```

@@

```{r regression_summary, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}
data <- proxyMR_comparison_summary_yiyp_adj_joint
summary(lm(rho_beta ~ omega_beta + 0, data = data))
summary(lm(gam_beta ~ omega_beta + 0, data = data))
summary(lm(gam_rho_beta ~ omega_beta + 0, data = data))
```

```{r resid_summary, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}
rho_resid <- resid(lm(rho_beta ~ gam_beta, data = data))
data$gam_rho_resid <- rho_resid + data$gam_beta
summary(lm(gam_rho_resid ~ omega_beta + 0, data = data))
```

```{r proxyMR_sig_gam_vs_omega, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), out.width = "200%", dpi=600, message = FALSE, warning = FALSE}

@@

```{r proxyMR_sig_rho_vs_omega, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), out.width = "200%", dpi=600, message = FALSE, warning = FALSE}

x_start <- "rho"
y_start <- "omega"
overlay_var_start <- "omega_vs_rho_BF_sig"
overlay_var = paste0(overlay_var_start)
